HGP analysis

### 2019-02-27 rick/1KGP.Rmd
update

```{r}
library(Matrix)
library(irlba)
library(threejs)
library(tidyverse)
library(lfa)
```

@@

@@

@@

```{r}
cm <- colMeans(chr20)
p <- irlba(chr20,
           nv=3,
           nu=3,
           tol=0.1,
           center=cm)
```

@@

```{r}
ggplot(bas_dt,
       aes(pc1, pc3, color=Population)) +
  geom_point() +
  theme_bw() 
```

@@

```{r}
chr20_mtx <- t(as.matrix(chr20[,1:50000]))
```

@@

@@

```{r}
subset <- af(chr20_mtx, LF)

subset[1:5,1]
```

>>>>

```{r}
library(Matrix)
library(irlba)
library(threejs)
library(tidyverse)
library(lfa)
library(furrr)
options(future.globals.maxSize= 10000000000)
plan(multicore)
```

@@

```{r}
rm(x)
gc()
```

@@

### work with a subset

```{r}
chr20_sub <- chr20[,1:100000]
```

@@

```{r}
cm <- colMeans(chr20_sub)
p <- irlba(chr20_sub,
           nv=3,
           nu=3,
           tol=0.1,
           center=cm)
```

@@

```{r}
ggplot(bas_dt,
       aes(pc1, pc2, color=Population)) +
  geom_point() +
  theme_bw() 
```

@@

```{r}
chr20_mtx <- t(as.matrix(chr20_sub))
```

@@

Determine genome-wide goodness-of-fit for a particular value of d by computing SNP-by-SNP goodness-of-fit when compared to population structure.

```{r}
#gof_4 <- model.gof(chr20_mtx, LF, 3)
#LF <- lfa(chr20_mtx, 10)
#gof_10 <- model.gof(chr20_mtx, LF, 3)
#hist(gof_4)
```

@@

```{r}
chr20sub_ial <- af(chr20_mtx, LF)

to_datalist <- function(i, data_genotype, data_iaf, qual){

    data <- tibble(genotype=data_genotype[i,],
               iaf=data_iaf[i,],
               qual=qual)

     return(data)       
}

fit_model_1 <- function(data){

  fit <- glm(genotype ~ qual + offset(iaf), family ="binomial", data=data)
  return(fit)

}

plot_data <- function(data){

      p <- ggplot(data,
       aes(qual, genotype, color=iaf)) +
      geom_point() +
      theme_bw()
  return(p)

}
```

loci <- c(1,4,5)
names(loci) <- loci

data_list <- map(loci, 
                 to_datalist,
                 data_genotype=chr20_mtx,
                 data_iaf=chr20sub_ial,
                 qual=bas_dt$avg_qual_mean)

```{r}
fits <- future_map(data_list, fit_model_1)

```{r}
plots <-  future_map(data_list, plot_data) 
```
